### 2019-03-18 papers/journal/encoding.tex
Update to bmc:02

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is very similar.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding slightly in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Hence, we will only present the stability encoding.  
%
Rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

In the $\fbmc$ encoding, the label of edges and nodes are represented as an array of bit vector of size $M$. 
%
For example, the bit vector \texttt{bvEdge}$[i][j][q]$ is the label is the $q$th edge between node $i$ and $j$.

% with each bit corresponding to the presence or absence of the molecule. 
%
%In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
%For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
%
%Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%
%The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
% 
%The molecule set is divided into Q and R-SNAREs. 
%
%For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
%An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
%
%Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
%
%Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
%
%For example, the variable \texttt{bvEdge}[1][2][1] = 1001, represents the first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
%
%Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
%
%We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%
%
The value of the bit vector describe the presence of the corresponding molecules at that particular location. 
%
For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
For example, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 1 and node 2.

>>>>

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Hence, we will only present the stability encoding.  
%
Rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

In the $\fbmc$ encoding, the label of the edges and nodes are represented by variables of type arrays of bit vector of size $M$. 
%
For example, the variable \texttt{bvEdge}$[i][j][q]$, represent the label of the $q$th edge between node $i$ and $j$.

% with each bit corresponding to the presence or absence of the molecule. 
%
%In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
%For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
%
%Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%
%The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
% 
%The molecule set is divided into Q and R-SNAREs. 
%
%For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
%An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
%
%Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
%
%Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
%
%For example, the variable \texttt{bvEdge}[1][2][1] = 1001, represents the first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
%
%Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
%
%We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%
%
The value of the bit vector variable describe the presence of the corresponding molecules at that particular location. 
%
For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
For example, the variable \texttt{bvEdge}[0][2][1] = $1001$, means the molecule  $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) are present on the first edge between node 2 and node 1.
